---
title: "Leaflet Map creation"
author: "Christian Lauritzen"
date: "2023-10-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Get the Libraries
Run these two things:
- install.packages("leaflet")
```{r}
library(leaflet)
```


Example with Markers on a map of Europe

First, create labels for your points

```{r}
popup = c("Robin", "Jakub", "Jannes")
```

You create a Leaflet map with these basic steps: you need to run the whole chain of course
```{r}
leaflet() %>%                                 # create a map widget by calling the library
  addProviderTiles("Esri.WorldPhysical") %>%  # add Esri World Physical map tiles
  addAwesomeMarkers(lng = c(-3, 23, 11),      # add layers, specified with longitude for 3 points
                    lat = c(52, 53, 49),      # and latitude for 3 points
                    popup = popup)            # specify labels, which will appear if you click on the point in the map
```


Let's look at Sydney with setView() function in Leaflet
```{r}
leaflet() %>%
  addTiles() %>%                              # add default OpenStreetMap map tiles
  addProviderTiles("Esri.WorldImagery",       # add custom Esri World Physical map tiles
                   options = providerTileOptions(opacity=0.5)) %>%     # make the Esri tile transparent
  setView(lng = 151.005006, lat = -33.9767231, zoom = 10)            # set the location of the map
```
 

Now let's refocus on Europe again
```{r}
leaflet() %>% 
  addTiles() %>% 
  setView( lng = 2.34, lat = 48.85, zoom = 5 ) %>%  # let's use setView to navigate to our area
  addProviderTiles("Esri.WorldPhysical", group = "Physical") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Aerial") %>% 
  addProviderTiles("MtbMap", group = "Geo") %>% 

addLayersControl(                                 # we are adding layers control to the maps
  baseGroups = c("Geo","Aerial", "Physical"),
  options = layersControlOptions(collapsed = T))
```
Click the box in topright corner in your Viewer to select between different background layers


#SYDNEY HARBOUR DISPLAY WITH LAYERS
Let's create a more complicated map 

Set the location and zoom level
```{r}
leaflet() %>% 
  setView(151.2339084, -33.85089, zoom = 13) %>%
  addTiles()  # checking I am in the right area
```

Bring in a choice of esri background layers  

Create a basic basemap
```{r}
l_aus <- leaflet() %>%   # assign the base location to an object
  setView(151.2339084, -33.85089, zoom = 13)
```

Now, prepare to select backgrounds
```{r}
esri <- grep("^Esri", providers, value = TRUE)
```

Select backgrounds from among provider tiles. To view them the options, 
go to https://leaflet-extras.github.io/leaflet-providers/preview/
```{r}
for (provider in esri) {
  l_aus <- l_aus %>% addProviderTiles(provider, group = provider)
}
```


Map of Sydney, NSW, Australia
We make a layered map out of the components above and write it to an object called AUSmap
```{r}
AUSmap <- l_aus %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
addControl("", position = "topright")
```

Run this to see your product
```{r}
AUSmap
```


#YOUR TASK NUMBER ONE

Task 1: Create a Danish equivalent of AUSmap with esri layers, but call it DANmap

Set the location and zoom level
```{r}
leaflet() %>% 
  setView(10.1996809, 56.1595891, zoom = 10) %>%
  addTiles()  # checking I am in the right area
```


Bring in a choice of esri background layers  
Create a basic basemap
```{r}
l_DK <- leaflet() %>%   # assign the base location to an object
  setView(10.1996809,56.1595891, zoom = 13)
```


Now, prepare to select backgrounds
```{r}
esri <- grep("^Esri", providers, value = TRUE)
```


Select backgrounds from among provider tiles. To view them the options, go to https://leaflet-extras.github.io/leaflet-providers/preview/
```{r}
for (provider in esri) {
  l_DK <- l_DK %>% addProviderTiles(provider, group = provider)
}
```


# Map of Aarhus, Denmark
We make a layered map out of the components above and write it to an object called Danmap
```{r}
Danmap <- l_DK %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")
```

run this to see your product
```{r}
Danmap
```



#ADD DATA TO LEAFLET

In this section you will manually create machine-readable spatial data from GoogleMaps: 

First, go to https://bit.ly/CreateCoordinates1
Enter the coordinates of your favorite leisure places in Denmark 
      extracting them from the URL in googlemaps, adding name and type of monument.
      Remember to copy the coordinates as a string, as just two decimal numbers separated by comma. 

Caveats: Do NOT edit the grey columns! They populate automatically!

Second, read the sheet into R. You will need gmail login information. 
      watch the console, it may ask you to authenticate or put in the number 
      that corresponds to the account you wish to use.

Libraries
```{r}
library(tidyverse)
library(googlesheets4)
library(leaflet)
```


Read in a Google sheet
```{r}
places <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=124710918",
                     col_types = "cccnncnc", range="DigitalMethods")
glimpse(places)
```


Load the coordinates in the map and check: are any points missing? Why?
```{r}
leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```


#########################################################


# Task 2: Read in the googlesheet data you and your colleagues populated with data into the DANmap object you created in Task 1.

```{r}
Danmap %>% 
  addControl("", position = "topright") %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```
I take the Danmap function from earlier and add this chunk of code which is what adds my markers at the longitude and latitude and names from the data document

# Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"
```{r}
Danmap  %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description,
             clusterOptions = markerClusterOptions())
```
I take the Danmap function from Task 2 and add the last line which sorts all my markers into clusters as i zoom out.

# Task 4: Look at the map and consider what it is good for and what not.
Giving a visual of points of interest on a map, and grouping them up if needed. This gives a good overlook of a possible big amount of points and helps us organise and sort them after location.
A problem could be that if you zoom too far out it becomes onclear where they are marking. There are spatial fuzziness slurring it a bit and making it slightly unreadable. 


# Task 5: Find out how to display notes and classifications in the map.
```{r}
Danmap %>% 
  addControl("", position = "topright") %>% 
  addCircles(lng = places$Longitude, 
             lat = places$Latitude,
             radius = sqrt(places$Stars1_5)*70,
             popup = places$Description)
```

Instead of using AddMarkers, i use AddCircles cause this gives me the ability to change size according to the data. I do this by defining the radius of circles by the amount of stars the point of interest has. 


